\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-08-12 article.tex
Added classification sub section to th eapproach

  Tagging movements in such a formalized manner enables us to retrieve the
  data we're interested in, using concepts from set theory.

% modelled the project in the database (./models)
%   explain all attributes etc.
% made a ruby script to parse the text files (link to bootstrap.rb ?)
%   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
%   saving the data into an sqlite3 database for analysis
%

>>>>

  % FIXME add database and ruby script info here
  % modelled the project in the database (./models)
  %   explain all attributes etc.
  % made a ruby script to parse the text files (link to bootstrap.rb ?)
  %   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
  %   saving the data into an sqlite3 database for analysis
  %

  Tagging movements in such a formalized manner, and registering it in a
  database, enables us to retrieve the data we're interested in using concepts
  from set theory.

\SubSection{Classification}

\begin{itemize}
  \item
    \emph{Yul-Gok Tul}
    \begin{itemize}
      \item
        {\bf Movement 24}, \emph{Gunnun so ap palkup bandae taerigi}, is
        tagged with $\{front\_strike\}$ due to the English description of
        striking with the right front elbow.
      \item
        {\bf Movement 27}, \emph{Gunnun so ap palkup bandae taerigi}, is
        tagged with $\{front\_strike\}$ due to the English description of
        striking with the left front elbow.
    \end{itemize}
  \item
    \emph{Joong-Gun Tul}
    \begin{itemize}
      \item
        {\bf Movement 8}, \emph{Gunnun so wipalkup taerigi}, is tagged
        $\{upper\_strike, \: upper\_elbow\}$ since the English description
        says that the movement is ``a right upper elbow strike.''
      \item
        {\bf Movement 10}, \emph{Gunnun so wipalkup taerigi}, is tagged
        $\{upper\_strike, \: upper\_elbow\}$ since the English description
        says that the movement is ``a left upper elbow strike.''
      \item
        {\bf Movement 11}, \emph{Gunnun so sang sewo jirugi}, is tagged as a
        left and right technique, with $\{left\_technique, \:
        right\_technique\}$.
      \item
        {\bf Movement 12}, \emph{Gunnun so sang dwijibo jirugi}, is tagged as
        a left and right technique, with $\{left\_technique, \:
        right\_technique\}$.
      \item
        {\bf Movement 27}, \emph{Nachuo so sonbadak noollo makgi}, is tagged
        as a $\{middle\_technique, \: low\_technique\}$ because the left hand
        is in the middle section and the right hand, forming the pressing
        block, is in the low section of the body. Furthermore, the movement
        has been tagged as a $\{right\_technique, \: left\_technique\}$ to
        reflect that both hands are being used.
      \item
        {\bf Movement 29}, \emph{Nachuo so sonbadak noollo makgi}, is tagged
        as a $\{middle\_technique, \: low\_technique\}$ because the right hand
        is in the middle section and the left hand, forming the pressing
        block, is in the low section of the body. Furthermore, the movement
        has been tagged as a $\{right\_technique, \: left\_technique\}$ to
        reflect that both hands are being used.
    \end{itemize}
  \item
    \emph{Choong-Moo Tul}
    \begin{itemize}
      \item
        {\bf Movement 19
    \end{itemize}
  \item
    \emph{Pragmatic}
    \begin{itemize}
      \item
        Free software is available for experimentation and testing.
      \item
        Most readers of this text have a background in relational technology. 
    \end{itemize}
\end{itemize}
